Chasing \rainbows with the Habitable Worlds Observatory

### 2023-02-24 src/tex/ms.tex
[showyourwork] overleaf sync

\renewcommand{\baselinestretch}{1.0} % Change to 1.65 for double spacing

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathrsfs}

@@

\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scaled=0.76]{beramono}
\usepackage{microtype}
\usepackage{csquotes}
\usepackage[capitalise]{cleveref}
\usepackage[dvipsnames, x11names]{xcolor}
\usepackage{xspace}

@@

\begin{figure*}%[t]
   \centering
   \includegraphics[width=\linewidth]{Fig1IWAPol.png}
   \caption{BOTT PLOT this is a holder until Kim updates the figure}
    \label{fig:bottplot}
\end{figure*}

@@

\begin{figure*}%[t]
   \centering
   \includegraphics[width=0.99\textwidth]{orb-grid.pdf}
   \caption{
        The scattering phase angles accessible to a direct imaging mission can be limited by orbital inclination or by the coronagraphic inner working angle. 
        If the orbital inclination is close to face-on (top panels) then the scattering phase angles probed throughout an orbit are limited by inclination; for circular orbits accessible scattering phases are $\phi \in 90^\circ \pm i$. 
        For orbital inclinations close to edge-on (bottom panels) the planet goes through all phases, but the scattering phase angles near 0$^\circ$ and 180$^\circ$ are not accessible due to obscuration by the coronagraph mask; for circular orbits, the accessible scattering phases are $\phi \in 90^\circ \pm \arcsin({\rm IWA}\cdot d_*/a)$.
    }
    \label{fig:orb-grid}
\end{figure*}

@@

\begin{figure}%[t]
    \centering
    % \includegraphics[width=\linewidth]{figures/scattering_angles.pdf}
    \includestandalone{figures/scattering-phase-angle}
    \caption{
        The angular separation, $\varepsilon$, of a planet orbiting with semi-major-axis $a$ about a star a distance $d_*$ from the observer. 
        The scattering phase angle is $\varphi$. 
        The smallest accessible scattering phase angle occurs when the angular separation equals the coronagraph inner working angle: $\varphi_{\rm min} = {\rm IWA} \cdot d_*/a$.
    }
    \label{fig:scattering_angles}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics{scatterplot.pdf}
    \caption{
        Scatter plot at 3 $\lambda/D$ for the target sample showing stellar effective temperature and stellar distance. 
        The size of the points represents the angular separation of the star and planet in milliarcseconds as presented in the target list. The colour of the points shows the atmospheric phenomenon that can be detected with darker colors including all lighter (yellow) color phenomenon. Thus dark blue points are systems which have the most key features, as systems in which the angles required to see the rainbow are probed will also have the angles required to see the Rayleigh scattering probed.
    }
    \label{fig:scatterplot}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{madness.pdf}  
    \caption{
        Eccentric orbits for the stellar sample $\IWA$ of 1, 2, 3 and 4~$\lambda / D$ corresponding to 21, 42, 63 and 84 mas.
        The habitable zone is identified in each panel. 
    }
    \label{fig:ball-o-yarn}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.6\textwidth]{features_plot_peak.png}  
    \caption{
        Number of systems vs inner working angle
    }
    \label{fig:accessible_phase_angles}
\end{figure*}

>>>>

\renewcommand{\baselinestretch}{1.0} % Change to 1.65 for double spacing
\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathrsfs}

@@

\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scaled=0.76]{beramono}
\usepackage{microtype}
\usepackage{csquotes}
\usepackage[capitalise]{cleveref}
%\usepackage[dvipsnames, x11names]{xcolor}
%\usepackage{xspace}

@@

\begin{figure*}%[t]
   \centering
   \includegraphics[width=\linewidth]{figures/Fig1IWAPol.png}
   \caption{BOTT PLOT this is a holder until Kim updates the figure}
    \label{fig:bottplot}
\end{figure*}

@@

\begin{figure*}%[t]
   \centering
   \includegraphics[width=0.99\textwidth]{figures/orb-grid.pdf}
   \caption{
        The scattering phase angles accessible to a direct imaging mission can be limited by orbital inclination or by the coronagraphic inner working angle. 
        If the orbital inclination is close to face-on (top panels) then the scattering phase angles probed throughout an orbit are limited by inclination; for circular orbits accessible scattering phases are $\phi \in 90^\circ \pm i$. 
        For orbital inclinations close to edge-on (bottom panels) the planet goes through all phases, but the scattering phase angles near 0$^\circ$ and 180$^\circ$ are not accessible due to obscuration by the coronagraph mask; for circular orbits, the accessible scattering phases are $\phi \in 90^\circ \pm \arcsin({\rm IWA}\cdot d_*/a)$.
    }
    \label{fig:orb-grid}
\end{figure*}

@@

%\begin{figure}%[t]
%    \centering
    % \includegraphics[width=\linewidth]{figures/scattering_angles.pdf}
%    \includestandalone{figures/scattering-phase-angle}
%    \caption{
%        The angular separation, $\varepsilon$, of a planet orbiting with semi-major-axis $a$ about a star a distance $d_*$ from the observer. 
%        The scattering phase angle is $\varphi$. 
%        The smallest accessible scattering phase angle occurs when the angular separation equals the coronagraph inner working angle: $\varphi_{\rm min} = {\rm IWA} \cdot d_*/a$.
%    }
%    \label{fig:scattering_angles}
%\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/scatterplot.pdf}
    \caption{
        Scatter plot at 3 $\lambda/D$ for the target sample showing stellar effective temperature and stellar distance. 
        The size of the points represents the angular separation of the star and planet in milliarcseconds as presented in the target list. The colour of the points shows the atmospheric phenomenon that can be detected with darker colors including all lighter (yellow) color phenomenon. Thus dark blue points are systems which have the most key features, as systems in which the angles required to see the rainbow are probed will also have the angles required to see the Rayleigh scattering probed.
    }
    \label{fig:scatterplot}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/madness.pdf}  
    \caption{
        Eccentric orbits for the stellar sample $\IWA$ of 1, 2, 3 and 4~$\lambda / D$ corresponding to 21, 42, 63 and 84 mas.
        The habitable zone is identified in each panel. 
    }
    \label{fig:ball-o-yarn}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.6\textwidth]{figures/features_plot_peak.png}  
    \caption{
        Number of systems vs inner working angle
    }
    \label{fig:accessible_phase_angles}
\end{figure*}
